Malacology: A Programmable Storage System

### 2016-10-21 paper/paper.tex
update
Signed-off-by: Noah Watkins <noahwatkins@gmail.com>

In Section~\ref{consistencyversioning-of-cluster-state} we described an
interface management service that is responsible for the durable and
consistent cluster-wide distribution of interface versions. We evaluate the
costs of such a service by embedding interface definitions in a Ceph cluster
membership data structure that is managed by a Paxos instance, and distributed
using a scalable, peer-to-peer gossip protocol that is built into Ceph. We
assume an architecture that consists of a light-weight interface that enforces
the semantics of interface management resulting in one or more interface
updates that must be consistent across the cluster. \paa{the word ``interface''
occurs too many times in the last sentence, but I'm not sure how to fix it.}
The following experiments
focus on the cost of distributing a consistent interface version.

\begin{figure}[h]
\centering
\includegraphics[trim={1 4 4 1.3cm},clip]{figures/iface-update-delay.pdf}
\caption{[\href{https://github.com/double-blind-submitter/osdi16}{source}]
Cluster-wide interface update latency, excluding the Paxos proposal cost for
interface commit. Each of the 120 OSDs used a RAM-based object store, while the
3 OSDs used an HDD-backed object store.}
\label{fig:propdelay}
\end{figure}

Figure~\ref{fig:propdelay} shows the CDF of the latency of installing and
distributing an interface update on all OSDs in the cluster. The latency is
defined as the elapsed time following the Paxos proposal for an interface
update until each OSD makes the update live (the cost of the Paxos proposal is
configurable and is discussed below). The latency measurements were taken on
the nodes running Ceph server daemons, and thus exclude the client round-trip
cost. In each of the experiments 1000 interface updates were observed.

The first experiment shown in Figure~\ref{fig:propdelay} illustrates a lower
bound cost for updates in a large cluster by avoiding disk I/O for storing
interface updates locally within each OSD.  In the experiment labeled "120 OSD
(RAM)" a cluster of 120 OSDs (10 OSDs x 12 servers) using an in-memory data
store were deployed, showing a latency of less than 54 ms with a probability
of 90\% and a worst case latency of 194 ms. The curve labeled "3 OSD (HDD)" 
\paa{DANGER -- didn't we delete this?}
is
a smaller cluster where each of the three OSDs uses a spinning disk as the
object store that saves a copy of the cluster map, and shows a latency of 37
ms with a 90\% probability and a worst case latency of 255 ms. Since the cost
of a disk I/O is larger than the same I/O executed against the in-memory
device, the predominant cost in a lightly loaded cluster appears to be the
number of OSDs.

\textbf{The Malacology Approach:} Re-use Ceph's Monitor functionality to
propagate application-specific state that needs to be highly-available and
strongly consistent.  The real cost of interface management, in addition to
cluster-wide propagation of interface updates, includes the network round-trip
to the interface management service, the Paxos commit protocol, and other
factors such as system load. By default Paxos proposals occur periodically with
a 1 second interval in order to accumulate updates. In a minimum, realistic
quorum of 3 monitors using HDD-based storage, we were able to decrease this
interval to an average of 222 ms.

>>>>

Domain-specific data interfaces (Section~\ref{object-data-interfaces}) allow
co-design between applications and the storage system. Malacology supports
custom object interfaces in RADOS that require interface implementations to
installed on the storage devices in the system, supports the evolution of
interfaces through automatic system-wide versioning and installation through
the service metdata interface (Section~\ref{service-metadata}). We evaluate
the performance of installing a new version of an interface in the cluster,
which is an important metric for applications that are designed with
frequently evolving interfaces.

We demonstrate the feasibility of utilizing the Ceph monitoring sub-system by
evaluating the performance of installing and distributing interface updates.
Figure~\ref{fig:propdelay} shows the CDF of the latency of interface updates.
The interfaces are Lua scripts embedded in the cluster map and distributed
using a peer-to-peer gossip protocol.  The latency is defined as the elapsed
time following the Paxos proposal for an interface update until each OSD makes
the update live (the cost of the Paxos proposal is configurable and is
discussed below). The latency measurements were taken on the nodes running
Ceph server daemons, and thus exclude the client round-trip cost. In each of
the experiments 1000 interface updates were observed.

Figure~\ref{fig:propdelay} shows the lower bound cost for updates in a large
cluster. In the experiment labeled "120 OSD (RAM)" a cluster of 120 OSDs (10
OSDs x 12 servers) using an in-memory data store were deployed, showing a
latency of less than 54 ms with a probability of 90\% and a worst case latency
of 194 ms. These costs demonstrate the penality of distributing the interface
in a large cluster. In In practice the costs are, in addition to cluster-wide
propagation of interface updates, includes the network round-trip to the
interface management service, the Paxos commit protocol, and other factors
such as system load. By default Paxos proposals occur periodically with a 1
second interval in order to accumulate updates. In a minimum, realistic quorum
of 3 monitors using HDD-based storage, we were able to decrease this interval
to an average of 222 ms.

\begin{figure}[h]
\centering
\includegraphics[trim={1 4 4 1.3cm},clip]{figures/iface-update-delay.pdf}
\caption{Cluster-wide interface update latency, excluding the Paxos proposal cost for
interface commit.}
\label{fig:propdelay}
\end{figure}
